Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-13 analysis/paper/paper.qmd
Table S3

We retained 3 NMDS axes for investigating the relationships between the environment and community structure of predators (stress = 0.135). Two variables, sampling year and ice coverage, were significantly correlated with the ordination scores (p = 0.002 and 0.013, respectively), although the effect size was small (r^2^ = 0.061 and 0.054, respectively; [@tbl-indicators]; see Table S3 for the coefficient, r^2^, and p-values of the environmental fit regression). The pack ice cluster occupied a wide range of values on NMDS axis 1, overlapping with the other 2 clusters ([@fig-nmds]). The marginal ice and open water clusters were well separated by NMDS axis 2.

@@

>>>>

We retained 3 NMDS axes for investigating the relationships between the environment and community structure of predators (stress = 0.135). Two variables, sampling year and ice coverage, were significantly correlated with the ordination scores (p = 0.002 and 0.013, respectively), although the effect size was small (r^2^ = 0.061 and 0.054, respectively; [@tbl-indicators]; see [@supptbl-nmds] for the coefficient, r^2^, and p-values of the environmental fit regression). The pack ice cluster occupied a wide range of values on NMDS axis 1, overlapping with the other 2 clusters ([@fig-nmds]). The marginal ice and open water clusters were well separated by NMDS axis 2.

@@

::: {#supptbl-nmds}
```{r}
make_tbl_nmdsdetail(read_obj("nmds_envfit"))

Direction cosines along the reduced dimensions (NMDS axes 1-3), goodness of fit ($r^2$), and significance ($p$) of the multiple regression analysis of environmental variables with respect to non-metric multidimensional scaling ordination scores. For descriptions of environmental variables, see [@tbl-envvar]. Statistically significant variables indicated with asterisk.
:::
